The \dealii Library, Version 9.6

### 2024-09-26 9.6/paper.tex
Address remaining TODOs.

In addition, there are three new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and that are intended as starting points for further
research rather than as teaching tools):
\todo[inline]{Marc Fehling: UPDATE ([W] Marc, you added this comment
  -- what did you want to update here? Perhaps add the affiliations of
the authors?)}
\begin{itemize}
  \item \emph{``Crystal growth phase field model''},
    contributed by Umair Hussain;
  \item \emph{``Nonlinear heat transfer problem''}, contributed by
    Narasimhan Swaminathan;
  \item \emph{``Traveling-wave solutions of a qualitative model for combustion waves''}, contributed by
    Shamil Magomedov.
\end{itemize}

@@

\todo[inline]{Marc: please insert allocation}

This work used [resource-name] at [resource provider] through allocation [allocation number] from the Advanced Cyberinfrastructure Coordination Ecosystem: Services \& Support (ACCESS) program, which is supported by National Science Foundation grants \#2138259, \#2138286, \#2138307, \#2137603, and \#2138296. See \cite{Boerner2023}.
\todo[inline]{Missing ACCESS information}

This work used the Extreme Science and Engineering Discovery Environment (XSEDE), which is supported by National Science Foundation grant number ACI-1053575 access through the CIG Science Gateway and Community Codes for the Geodynamics Community MCA08X011 allocation.

>>>>

In addition, there are three new programs in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and that are intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item \emph{``Crystal growth phase field model''},
    contributed by Umair Hussain;
  \item \emph{``Nonlinear heat transfer problem''}, contributed by
    Narasimhan Swaminathan;
  \item \emph{``Traveling-wave solutions of a qualitative model for combustion waves''}, contributed by
    Shamil Magomedov.
\end{itemize}

@@

This work used the \textit{Expanse} HPC system at the San Diego Supercomputer Center (SDSC) at UC San Diego through the CIG Science Gateway and Community Codes for the Geodynamics Community MCA08X011 allocation from the Advanced Cyberinfrastructure Coordination Ecosystem: Services \& Support (ACCESS) program, which is supported by National Science Foundation grants \#2138259, \#2138286, \#2138307, \#2137603, and \#2138296. See \cite{Boerner2023}.
